Hadoop Image Processing Framework

### 2015-03-13 Paper.tex
cited references in introduction

	When considering operations such as face detection, image classification\cite{Li2009} and other types of processing on images, there are limits on what can be done to improve performance of single computers to make them able to process information at the scale of social media. Therefore, the advantages of parallel distributed processing of a large image dataset by using the computational resources of a cloud computing environment should be considered. In addition, if computational resources can be secured easily and relatively inexpensively, then cloud computing is suitable for handling large image data sets at very low cost and increased performance. Hadoop, as a system for processing large numbers of images by parallel and distributed computing, seems promising. In fact, Hadoop is in use all over the world. Studies using Hadoop have been performed, dealing with text data files, analyzing large volumes of DNA sequence data, converting the data of a large number of still images to PDF format, and carrying out feature selection/extraction in astronomy. %Cite the papers in which these examples appear
These examples demonstrate the usefulness of the Hadoop system, which can run multiple processes in parallel for load balancing and task management.

@@

\section{Conclusion}
This paper has decribed our framework fo image processing for large scale image processing applications on the MapReduce framework. The framework is designed to abstract the technical details of Hadoop's powerful MapReduce framework and provide a way for users who want to process large image datasets. We provided a how the images can be stored in different hadoop file format and efficient access within Map Reduce pipeline and simple modules to make the framework more easier. By providing interoperability between different image data types we give the user to process the images using different open-source image processing libraries. Finally, we provide a way to overcome the loss of image headers after processing which are most useful for image processing and vision applications.

>>>>

	When considering operations such as face detection, image classification\cite{Li2009} and other types of processing on images, there are limits on what can be done to improve performance of single computers to make them able to process information at the scale of social media. Therefore, the advantages of parallel distributed processing of a large image dataset by using the computational resources of a cloud computing environment should be considered. In addition, if computational resources can be secured easily and relatively inexpensively, then cloud computing is suitable for handling large image data sets at very low cost and increased performance. Hadoop, as a system for processing large numbers of images by parallel and distributed computing, seems promising. In fact, Hadoop is in use all over the world. Studies using Hadoop have been performed, dealing with text data files\cite{Lin2010}, analyzing large volumes of DNA sequence data\cite{McKenna2010}, converting the data of a large number of still images to PDF format, and carrying out feature selection/extraction in astronomy\cite{wiley2011}. %Cite the papers in which these examples appear
These examples demonstrate the usefulness of the Hadoop system, which can run multiple processes in parallel for load balancing and task management.

@@

\section{Conclusion}
This paper has described our framework fo image processing for large scale image processing applications on the MapReduce framework. The framework is designed to abstract the technical details of Hadoop's powerful MapReduce framework and provide a way for users who want to process large image datasets. We provided a how the images can be stored in different hadoop file format and efficient access within Map Reduce pipeline and simple modules to make the framework more easier. By providing interoperability between different image data types we give the user to process the images using different open-source image processing libraries. Finally, we provide a way to overcome the loss of image headers after processing which are most useful for image processing and vision applications.
